### 2018-03-13 doc/manuscript.Rmd
minor edit to title
rearrange abbrev

Title (109 / 110 characters): 
Clusters of fatty acids in serum triacylglyceride fraction associate with the
pathogenesis of type 2 diabetes

@@

- TGFA: Triacylglycerol fatty acids
- IS: Insulin sensitivity
- PROMISE: Prospective Metabolism and Islet Cell Evaluation cohort
- ISI: Insulin sensitivity index
- GEE: Generalized estimating equations
- PLS: Partial least squares
- HOMA2-%S: Homeostatic model of assessment 2 - percent sensitivity
- IGI/IR: Insulinogenic index over homeostatic model of assessment for insulin
resistance
- ISSI-2: Insulin Secretion-Sensitivity Index-2
- DNL: De novo lipogenesis
- ALT: Alanine aminotransferase
- NEFA: Non-esterified fatty acids
- OGTT: Oral glucose tolerance test
- CV: Coefficient of variation
- MAQ: Modified activity questionnaire
- WC: Waist circumference
- MET: Metabolic equivalent of task
- SD: Standard deviation

>>>>

Title (110 / 110 characters): 
Clusters of fatty acids in the serum triacylglyceride fraction associate with the
disorders of type 2 diabetes

@@

- ALT: Alanine aminotransferase
- CV: Coefficient of variation
- DNL: De novo lipogenesis
- GEE: Generalized estimating equations
- HOMA2-%S: Homeostatic model of assessment 2 - percent sensitivity
- IGI/IR: Insulinogenic index over homeostatic model of assessment for insulin
resistance
- IS: Insulin sensitivity
- ISI: Insulin sensitivity index
- ISSI-2: Insulin Secretion-Sensitivity Index-2
- MAQ: Modified activity questionnaire
- MET: Metabolic equivalent of task
- NEFA: Non-esterified fatty acids
- OGTT: Oral glucose tolerance test
- PROMISE: Prospective Metabolism and Islet Cell Evaluation cohort
- PLS: Partial least squares
- SD: Standard deviation
- TGFA: Triacylglycerol fatty acids
- WC: Waist circumference
